Scoring epidemiological forecasts on transformed scales

### 2023-08-15 final submission after reformatting/final-manuscript.tex
Remove cross-references in manuscript

where $y$ is the true observed value, $F$ is the cumulative distribution function (CDF) of the predictive distribution, and $\boldsymbol{1}()$ is the indicator function. The CRPS can be understood as a generalisation of the absolute error to predictive distributions, and interpreted on the natural scale of the data. The WIS is an approximation of the CRPS for predictive distributions represented by a set of predictive quantiles and is currently used to assess forecasts in the so-called COVID-19 Forecast Hubs in the US \cite{cramerCOVID19ForecastHub2020, cramerEvaluationIndividualEnsemble2021}, Europe \cite{sherrattPredictivePerformanceMultimodel2022} and Germany and Poland \cite{bracherShorttermForecastingCOVID192021, bracherNationalSubnationalShortterm2021}, as well as the US \textit{FluSight} project on influenza forecasting\cite{CdcepiFlusightforecastdata2022}. The WIS is defined as 
\begin{linenomath*}
\begin{equation}
    \text{WIS}(F, y) = \frac{1}{K} \times \sum_{k = 1}^{K} 2 \times \left[ \boldsymbol{1}(y \leq q_{\tau_k}) - \tau_k \right] \times ( q_{\tau_k} - y), 
\end{equation}
\end{linenomath*}
where $q_{\tau}$ is the $\tau$ quantile of the forecast $F$, $y$ is the observed outcome and $K$ is the number of (roughly equally spaced) predictive quantiles provided. The WIS can be decomposed into three components, dispersion, underprediction and overprediction, which reflect the spread of the forecast and whether it was centred above or below the observed value. We show an alternative definition based on central prediction intervals in Supplement \ref{sec:alternative-wis} which illustrates this decomposition.

@@

In many fields, it is common practice to forecast transformed quantities (see e.g. \cite{taylorEvaluatingVolatilityInterval1999} in finance, \cite{mayrLogLevelVAR2015} in macroeconomics, \cite{loweStochasticRainfallrunoffForecasting2014} in hydrology or \cite{fuglstadDoesNonstationarySpatial2015} in meteorology). While the goal of the transformations is often to improve the accuracy of the predictions, they can also be used to enhance and complement the evaluation process. 
In this paper, we argue that the aforementioned issues with evaluating epidemic forecasts based on measures of absolute error on the natural scale can be addressed by transforming the forecasts and observations prior to scoring using some strictly monotonic transformation. Strictly monotonic transformations can shift the focus of the evaluation in a way that may be more appropriate for epidemiological forecasts, while guaranteeing that the score remains proper. Many different transformations may be appropriate and useful, depending on the exact context, the desired focus of the evaluation, and specific aspects forecast consumers care most about (see a broader discussion in Section \ref{sec:discussion}).

For conceptual clarity and to allow for a more in-depth discussion, we focus mostly on the natural logarithm as a particularly attractive transformation in the context of epidemic phenomena. We refer to this transformation as 'log-transformation' and to scores that have been computed from log-transformed forecasts and observations as scores 'on the log scale' (as opposed to scores 'on the natural scale', which involve no transformation). In the theoretical discussion in Section \ref{sec:methods}, 'log-transformation' and 'log scale' generally refer to a transformation of $\log_{e}(x)$. For practical applications (Section \ref{sec:HUB}) we also use these terms to describe a transformation of $\log_{e}(x + a)$ with a small $a > 0$ in order to keep the terminology and notation simple. For a prediction target with strictly positive support, the CRPS after applying a log-transformation is given by
%
\begin{linenomath*}
\begin{equation}
    \text{CRPS}(F_{\log}, \log y) = \int_{-\infty}^\infty \left( F_{\log}(x) - \boldsymbol{1}(x \geq \log y) \right)^2 dx.
\end{equation}    
\end{linenomath*}
%
Here, $y$ is again the observed outcome and $F_{\log}$ is the predictive CDF of the log-transformed outcome, i.e.,
\begin{linenomath*}
\begin{equation}
F_{\log}(x) = F(\exp(x)),
\end{equation}    
\end{linenomath*}
with $F$ the CDF on the original scale. Instead of a score representing the magnitude of absolute errors, applying a log-transformation prior to the CRPS yields a score which a) measures relative error (see Section \ref{sec:methods:relative}), b) provides a measure for how well a forecast captures the exponential growth rate of the target quantity (see Section \ref{sec:methods:growthrate}) and c) is less dependent on the expected order of magnitude of the quantity to be predicted (see Section \ref{sec:methods:vst}). 
We therefore argue that such evaluations on the logarithmic scale should complement the prevailing evaluations on the natural scale. 
Other transformations may likewise be of interest. We briefly explore the square root transformation as an alternative transformation. 
Our analysis mostly focuses on the CRPS (or WIS) as an evaluation metric for probabilistic forecasts, given its widespread use throughout the COVID-19 pandemic. We note that the logarithmic score has scale invariance properties which imply that score differences between different forecasts are invariant to strictly monotonic transformations (see \cite{Lehmann1950} on corresponding properties of likelihood ratios and \cite{diksLikelihoodbasedScoringRules2011}). The question of the right scale to evaluate forecasts on does therefore not arise for the log score.

The remainder of the article is structured as follows. In Sections \ref{sec:methods:relative}--\ref{sec:methods:vst} we provide some mathematical intuition on applying the log-transformation prior to evaluating the CRPS, highlighting the connections to relative error measures, the epidemic growth rate and variance stabilizing transformations.
We then discuss the effect of the log-transformation on forecast rankings (Section \ref{sec:methods:rankings}) as well as practical considerations for applying transformations in general and the log-transformation in particular (Section \ref{sec:methods:considerations}). To analyse the real-world implications of the log-transformation we use forecasts submitted to the European COVID-19 Forecast Hub  (\cite{europeancovid-19forecasthubEuropeanCovid19Forecast2021,sherrattPredictivePerformanceMultimodel2022}, Section \ref{sec:HUB}). Finally, we provide scoring recommendations, discuss alternative transformations that may be useful in different contexts, and suggest further research avenues (Section \ref{sec:discussion}).

@@

\begin{linenomath*}
\begin{equation}
\mathbb{E}_F[\text{CRPS}\{F_{\log}, \log(y)\}] \approx \frac{\sigma/\mu}{\sqrt{\pi}} 
= \frac{\sqrt{c}}{\sqrt{\pi}}
.\label{eq:taylor_quadratic}
\end{equation}
\end{linenomath*}
As $\sigma$ and $\mu$ are linked through the quadratic mean-variance relationship (or linear mean-standard deviation relationship, $\sigma = \sqrt{c} \times \mu$), the expected CRPS thus stays constant regardless of the expected value of the data-generating distribution $\mu$. The assumption of a quadratic mean-variance relationship is closely linked to the aspects discussed in Sections \ref{sec:methods:relative} and \ref{sec:methods:growthrate}. It implies that relative errors have constant variance and can thus be meaningfully compared across different targets. Also, it arises naturally if we assume that our capacity to predict the epidemic growth rate does not depend on the expected outcome, i.e. does not depend on the current phase of the epidemic or the order of magnitude of current observations.

@@

\subsection*{Effects on model rankings}
\label{sec:methods:rankings}
Rankings between different forecasters based on the CRPS may change when making use of a transformation, both in terms of aggregate and individual scores. We illustrate this in Fig \ref{fig:illustration-ranking} with two forecasters, A and B, issuing two different distributions with different dispersion. When showing the obtained CRPS as a function of the observed value, it can be seen that the ranking between the two forecasters may change when scoring the forecast on the logarithmic, rather than the natural scale. In particular, on the natural scale, forecaster A, who issues a more uncertain distribution, receives a better score than forecaster B for observed values far away from the centre of the respective predictive distribution. On the log scale, however, forecaster A receives a lower score for large observed values, being more heavily penalised for assigning large probability to small values (which, in relative terms, are far away from the actual observation). We note that the chosen example involving a geometric forecast distribution is somewhat constructed; as shown in Section \ref{sec:Hub:cor} and Fig \ref{fig:HUB-cors}A, rankings between models in practice stay quite stable for a single forecast.

@@

In practice, one issue with the log transform is that it is not readily applicable to negative or zero values, which need to be removed or otherwise handled. 
One common approach to this end is to add a small positive quantity, such as $a = 1$, to all observations and predictions before taking the logarithm \cite{bellegoDealingLogsZeros2022}. This still represents a strictly monotonic transformation, but the choice of $a$ does influence scores and rankings (measures of relative errors shrink the larger the chosen value $a$). As a rule of thumb, if if $x > 5a$, the difference between $\log{(x + a)}$ and $\log{(x)}$ is small, and it becomes negligible if $x > 50a$. Choosing a suitable offset $a$ thus balances two competing concerns: on the one hand, choosing a small $a$ makes sure that the transformation is as close to a natural logarithm as possible and scores can be interpreted as outlined in the previous sections. On the other hand, choosing a larger $a$ can help stabilise scores for forecasts and observations close to zero, avoiding giving excessive weight to forecasts of small quantities. For increasing $a$, less relative weight is given to smaller forecast targets. For very large values of $a$, $\log(x + a)$ is roughly linear in $x$, so that using a very large $a$ implies similar relative weighting as applying no transformation at all. In practice, a user could explore the effect of different values of $a$ graphically and choose $a$ such that the relative weightings of times and regions with high and low incidence correspond to their preferences (see Fig \ref{fig:HUB-log-different-offsets} in our example application, Section \ref{sec:HUB}).

@@

Some other strictly monotonic transformations that can be applied are scaling by the population size or scaling by past observations. The latter, as discussed in Section \ref{sec:discussion}, is similar to applying a log-transformation, but corresponds to evaluating a forecast of multiplicative, rather than exponential growth rates. The arising issue of dividing by zero can again be solved by adding a small offset $a$. Scaling a forecast by the later observed value (as opposed to scaling by past observations) is generally not permissible as it can result in improper scores (see \cite{lerchForecasterDilemmaExtreme2015} on the closely related topic of weighting scores with a function of the observed value). Similarly, scaling forecasts and observations by a function of the predictive distribution (like the predictive mean) may lead to improper scores; however, we are unaware of existing theoretical arguments on this.

@@

We note that in the practical evaluation of operational forecasting systems  several additional challenges arise, which we do not study in detail. These concern e.g., the removal of outlying observations and forecasts and the handling of missing forecasts. The solutions we employed in practice are provided in Section \ref{sec:HUB-setting}.

@@

\begin{figure}[h!]
    \centering
    \caption{
    Forecasts and scores for two-week-ahead predictions from the EuroCOVIDhub-ensemble made in Germany. Missing values are due to data anomalies that were removed (see section \ref{sec:HUB-setting}. 
    A, E: 50\% and 90\% prediction intervals and observed values for cases and deaths on the natural scale. B, F: Corresponding scores. C, G: Forecasts and observations on the log scale. D, H: Corresponding scores. 
    }
    \label{fig:HUB-model-comparison-ensemble}
\end{figure}

@@

Across the dataset, the average number of observed cases and deaths varied considerably by location and target type (see Fig \ref{fig:HUB-mean-locations}A and B). On the natural scale, scores show a pattern quite similar to the observations across targets (see Fig \ref{fig:HUB-mean-locations}D) and locations (see Fig \ref{fig:HUB-mean-locations}C). On the log scale, scores were more evenly distributed between targets (see Fig \ref{fig:HUB-mean-locations}D) and locations (see Fig \ref{fig:HUB-mean-locations}C). Both on the natural scale as well on the log scale, scores increased considerably with increasing forecast horizon (see Fig \ref{fig:HUB-mean-locations}E). This reflects the increasing difficulty of forecasts further into the future and, for the log scale, corresponds with our expectations from Section \ref{sec:methods:growthrate}.

To assess the impact of the choice of offset value $a$ we extend the display from Fig \ref{fig:HUB-mean-locations}C by results obtained under different specifications. Results are shown in Fig \ref{fig:HUB-log-different-offsets}, where for completeness we also added the square root transformation. As discussed in Section \ref{sec:methods:considerations}, smaller values of $a$ increase the relative weight of smaller locations in the overall evaluation. In the most extreme considered case $a = 0.001$, the smallest locations in fact receive the largest weight both for deaths and cases. For very large values (see the third row of Fig \ref{fig:HUB-log-different-offsets}), the relative weights strongly resemble those of the evaluation on the natural scale. We recommend using displays of this type to get an intuition for the role different locations may play for overall evaluation results.

@@

As argued in Section \ref{sec:methods:vst}, the mean-variance, or mean-CRPS, relationship determines which transformation can serve as a VST. We can analyse this relationship empirically by running a regression that explains the WIS (which approximates the CRPS) as a function of the central estimate of the predictive distribution. We ran the regression
\begin{linenomath*}
\begin{equation}
    \log[\text{WIS}(F, y)] = \alpha + \beta \times \log[\text{median}(F)], 
\end{equation}
\end{linenomath*}
where the predictive distribution $F$ and the observation $y$ are on the natural scale. This is equivalent to
\begin{linenomath*}
\begin{equation}
    \text{WIS}(F, y) = \exp(\alpha) \times \text{median}(F)^\beta, 
\end{equation}
\end{linenomath*}
meaning that we estimate a polynomial relationship between the predictive median and achieved WIS. Note that we are using predictive medians rather than means as only the former are available in the European COVID-19 Forecast Hub. As (under the simplifying assumption of normality; see Section \ref{sec:methods:vst}) the WIS/CRPS of an ideal forecaster scales with the standard deviation, a value of $\beta = 1$ would imply a quadratic median-variance relationship; the natural logarithm could then serve as a VST. A value of $\beta = 0.5$ would imply a linear median-variance relationship, suggesting the square root as a VST. We applied the regression to case and death forecasts, stratified for one through four-week-ahead forecasts. Results are provided in Table \ref{tab:HUB-regression}. It can be seen that the estimates of $\beta$ always take a value somewhat below 1, implying a slightly sub-quadratic mean-variance relationship. The logarithmic transformation should thus approximately stabilize the variance (and WIS), possibly leading to somewhat higher scores for smaller forecast targets. The square-root transformation, on the other hand, can be expected to still lead to higher WIS values for targets of higher orders of magnitude.

\begin{figure}[h!]
    \centering
    \caption{Relationship between median forecasts and scores. Black dots represent WIS values for two-week ahead predictions of the EuroCOVIDhub-ensemble. Shown in red are the regression lines discussed in Section \ref{sec:HUB-regression} shown in Table \ref{tab:HUB-regression}. A: WIS for two-week-ahead predictions of the EuroCOVIDhub-ensemble against median predicted values. B: Same as A, with scores obtained after applying a square-root-transformation to the data. C: Same as A, with scores obtained after applying a log-transformation to the data.} 
    \label{fig:HUB-regression}
\end{figure}

@@

\paragraph{S3 Fig.}
\label{fig:score-approx}
\textbf{Visualisation of expected CRPS values against approximated scores.} 
This is using the approximation detailed in Section \ref{sec:methods:rankings} (see also Fig \ref{fig:SIM-wis-state-size-mean}). Expected CRPS scores are shown for three different distributions once on the natural scale (top row) and once scored on the log scale (bottom row).

>>>>

where $y$ is the true observed value, $F$ is the cumulative distribution function (CDF) of the predictive distribution, and $\boldsymbol{1}()$ is the indicator function. The CRPS can be understood as a generalisation of the absolute error to predictive distributions, and interpreted on the natural scale of the data. The WIS is an approximation of the CRPS for predictive distributions represented by a set of predictive quantiles and is currently used to assess forecasts in the so-called COVID-19 Forecast Hubs in the US \cite{cramerCOVID19ForecastHub2020, cramerEvaluationIndividualEnsemble2021}, Europe \cite{sherrattPredictivePerformanceMultimodel2022} and Germany and Poland \cite{bracherShorttermForecastingCOVID192021, bracherNationalSubnationalShortterm2021}, as well as the US \textit{FluSight} project on influenza forecasting\cite{CdcepiFlusightforecastdata2022}. The WIS is defined as 
\begin{linenomath*}
\begin{equation}
    \text{WIS}(F, y) = \frac{1}{K} \times \sum_{k = 1}^{K} 2 \times \left[ \boldsymbol{1}(y \leq q_{\tau_k}) - \tau_k \right] \times ( q_{\tau_k} - y), 
\end{equation}
\end{linenomath*}
where $q_{\tau}$ is the $\tau$ quantile of the forecast $F$, $y$ is the observed outcome and $K$ is the number of (roughly equally spaced) predictive quantiles provided. The WIS can be decomposed into three components, dispersion, underprediction and overprediction, which reflect the spread of the forecast and whether it was centred above or below the observed value. We show an alternative definition based on central prediction intervals in \nameref{sec:alternative-wis} which illustrates this decomposition.

@@

In many fields, it is common practice to forecast transformed quantities (see e.g. \cite{taylorEvaluatingVolatilityInterval1999} in finance, \cite{mayrLogLevelVAR2015} in macroeconomics, \cite{loweStochasticRainfallrunoffForecasting2014} in hydrology or \cite{fuglstadDoesNonstationarySpatial2015} in meteorology). While the goal of the transformations is often to improve the accuracy of the predictions, they can also be used to enhance and complement the evaluation process. 
In this paper, we argue that the aforementioned issues with evaluating epidemic forecasts based on measures of absolute error on the natural scale can be addressed by transforming the forecasts and observations prior to scoring using some strictly monotonic transformation. Strictly monotonic transformations can shift the focus of the evaluation in a way that may be more appropriate for epidemiological forecasts, while guaranteeing that the score remains proper. Many different transformations may be appropriate and useful, depending on the exact context, the desired focus of the evaluation, and specific aspects forecast consumers care most about (see Discussion).

For conceptual clarity and to allow for a more in-depth discussion, we focus mostly on the natural logarithm as a particularly attractive transformation in the context of epidemic phenomena. We refer to this transformation as 'log-transformation' and to scores that have been computed from log-transformed forecasts and observations as scores 'on the log scale' (as opposed to scores 'on the natural scale', which involve no transformation). In the theoretical part of the paper, 'log-transformation' and 'log scale' generally refer to a transformation of $\log_{e}(x)$. For practical applications in the later sections we also use these terms to describe a transformation of $\log_{e}(x + a)$ with a small $a > 0$ in order to keep the terminology and notation simple. For a prediction target with strictly positive support, the CRPS after applying a log-transformation is given by
%
\begin{linenomath*}
\begin{equation}
    \text{CRPS}(F_{\log}, \log y) = \int_{-\infty}^\infty \left( F_{\log}(x) - \boldsymbol{1}(x \geq \log y) \right)^2 dx.
\end{equation}    
\end{linenomath*}
%
Here, $y$ is again the observed outcome and $F_{\log}$ is the predictive CDF of the log-transformed outcome, i.e.,
\begin{linenomath*}
\begin{equation}
F_{\log}(x) = F(\exp(x)),
\end{equation}    
\end{linenomath*}
with $F$ the CDF on the original scale. Instead of a score representing the magnitude of absolute errors, applying a log-transformation prior to the CRPS yields a score which a) measures relative error, b) provides a measure for how well a forecast captures the exponential growth rate of the target quantity and c) is less dependent on the expected order of magnitude of the quantity to be predicted). 
We therefore argue that such evaluations on the logarithmic scale should complement the prevailing evaluations on the natural scale. 
Other transformations may likewise be of interest. We briefly explore the square root transformation as an alternative transformation. 
Our analysis mostly focuses on the CRPS (or WIS) as an evaluation metric for probabilistic forecasts, given its widespread use throughout the COVID-19 pandemic. We note that the logarithmic score has scale invariance properties which imply that score differences between different forecasts are invariant to strictly monotonic transformations (see \cite{Lehmann1950} on corresponding properties of likelihood ratios and \cite{diksLikelihoodbasedScoringRules2011}). The question of the right scale to evaluate forecasts on does therefore not arise for the log score.

The remainder of the article is structured as follows. First, we provide some mathematical intuition on applying the log-transformation prior to evaluating the CRPS, highlighting the connections to relative error measures, the epidemic growth rate and variance stabilizing transformations.
We then discuss the effect of the log-transformation on forecast rankings as well as practical considerations for applying transformations in general and the log-transformation in particular. To analyse the real-world implications of the log-transformation we use forecasts submitted to the European COVID-19 Forecast Hub  \cite{europeancovid-19forecasthubEuropeanCovid19Forecast2021,sherrattPredictivePerformanceMultimodel2022}. Finally, we provide scoring recommendations, discuss alternative transformations that may be useful in different contexts, and suggest further research avenues).

@@

\begin{linenomath*}
\begin{equation}
\mathbb{E}_F[\text{CRPS}\{F_{\log}, \log(y)\}] \approx \frac{\sigma/\mu}{\sqrt{\pi}} 
= \frac{\sqrt{c}}{\sqrt{\pi}}
.\label{eq:taylor_quadratic}
\end{equation}
\end{linenomath*}
As $\sigma$ and $\mu$ are linked through the quadratic mean-variance relationship (or linear mean-standard deviation relationship, $\sigma = \sqrt{c} \times \mu$), the expected CRPS thus stays constant regardless of the expected value of the data-generating distribution $\mu$. The assumption of a quadratic mean-variance relationship is closely linked to the aspects discussed earlier. It implies that relative errors have constant variance and can thus be meaningfully compared across different targets. Also, it arises naturally if we assume that our capacity to predict the epidemic growth rate does not depend on the expected outcome, i.e. does not depend on the current phase of the epidemic or the order of magnitude of current observations.

@@

\subsection*{Effects on model rankings}
\label{sec:methods:rankings}
Rankings between different forecasters based on the CRPS may change when making use of a transformation, both in terms of aggregate and individual scores. We illustrate this in Fig \ref{fig:illustration-ranking} with two forecasters, A and B, issuing two different distributions with different dispersion. When showing the obtained CRPS as a function of the observed value, it can be seen that the ranking between the two forecasters may change when scoring the forecast on the logarithmic, rather than the natural scale. In particular, on the natural scale, forecaster A, who issues a more uncertain distribution, receives a better score than forecaster B for observed values far away from the centre of the respective predictive distribution. On the log scale, however, forecaster A receives a lower score for large observed values, being more heavily penalised for assigning large probability to small values (which, in relative terms, are far away from the actual observation). We note that the chosen example involving a geometric forecast distribution is somewhat constructed; as shown in Fig \ref{fig:HUB-cors}A, rankings between models in practice stay quite stable for a single forecast.

@@

In practice, one issue with the log transform is that it is not readily applicable to negative or zero values, which need to be removed or otherwise handled. 
One common approach to this end is to add a small positive quantity, such as $a = 1$, to all observations and predictions before taking the logarithm \cite{bellegoDealingLogsZeros2022}. This still represents a strictly monotonic transformation, but the choice of $a$ does influence scores and rankings (measures of relative errors shrink the larger the chosen value $a$). As a rule of thumb, if if $x > 5a$, the difference between $\log{(x + a)}$ and $\log{(x)}$ is small, and it becomes negligible if $x > 50a$. Choosing a suitable offset $a$ thus balances two competing concerns: on the one hand, choosing a small $a$ makes sure that the transformation is as close to a natural logarithm as possible and scores can be interpreted as outlined in the previous sections. On the other hand, choosing a larger $a$ can help stabilise scores for forecasts and observations close to zero, avoiding giving excessive weight to forecasts of small quantities. For increasing $a$, less relative weight is given to smaller forecast targets. For very large values of $a$, $\log(x + a)$ is roughly linear in $x$, so that using a very large $a$ implies similar relative weighting as applying no transformation at all. In practice, a user could explore the effect of different values of $a$ graphically and choose $a$ such that the relative weightings of times and regions with high and low incidence correspond to their preferences (see Fig \ref{fig:HUB-log-different-offsets} in our example application).

@@

Some other strictly monotonic transformations that can be applied are scaling by the population size or scaling by past observations. The latter is similar to applying a log-transformation, but corresponds to evaluating a forecast of multiplicative, rather than exponential growth rates. The arising issue of dividing by zero can again be solved by adding a small offset $a$. Scaling a forecast by the later observed value (as opposed to scaling by past observations) is generally not permissible as it can result in improper scores (see \cite{lerchForecasterDilemmaExtreme2015} on the closely related topic of weighting scores with a function of the observed value). Similarly, scaling forecasts and observations by a function of the predictive distribution (like the predictive mean) may lead to improper scores; however, we are unaware of existing theoretical arguments on this.

@@

We note that in the practical evaluation of operational forecasting systems  several additional challenges arise, which we do not study in detail. These concern e.g., the removal of outlying observations and forecasts and the handling of missing forecasts. The solutions we employed in practice are detailed below.

@@

\begin{figure}[h!]
    \centering
    \caption{
    Forecasts and scores for two-week-ahead predictions from the EuroCOVIDhub-ensemble made in Germany. Missing values are due to data anomalies that were removed. 
    A, E: 50\% and 90\% prediction intervals and observed values for cases and deaths on the natural scale. B, F: Corresponding scores. C, G: Forecasts and observations on the log scale. D, H: Corresponding scores. 
    }
    \label{fig:HUB-model-comparison-ensemble}
\end{figure}

@@

Across the dataset, the average number of observed cases and deaths varied considerably by location and target type (see Fig \ref{fig:HUB-mean-locations}A and B). On the natural scale, scores show a pattern quite similar to the observations across targets (see Fig \ref{fig:HUB-mean-locations}D) and locations (see Fig \ref{fig:HUB-mean-locations}C). On the log scale, scores were more evenly distributed between targets (see Fig \ref{fig:HUB-mean-locations}D) and locations (see Fig \ref{fig:HUB-mean-locations}C). Both on the natural scale as well on the log scale, scores increased considerably with increasing forecast horizon (see Fig \ref{fig:HUB-mean-locations}E). This reflects the increasing difficulty of forecasts further into the future and, for the log scale, corresponds with our expectations based on the theoretical considerations detailed above.

To assess the impact of the choice of offset value $a$ we extend the display from Fig \ref{fig:HUB-mean-locations}C by results obtained under different specifications. Results are shown in Fig \ref{fig:HUB-log-different-offsets}, where for completeness we also added the square root transformation. Smaller values of $a$ increase the relative weight of smaller locations in the overall evaluation. In the most extreme considered case $a = 0.001$, the smallest locations in fact receive the largest weight both for deaths and cases. For very large values (see the third row of Fig \ref{fig:HUB-log-different-offsets}), the relative weights strongly resemble those of the evaluation on the natural scale. We recommend using displays of this type to get an intuition for the role different locations may play for overall evaluation results.

@@

As argued above, the mean-variance, or mean-CRPS, relationship determines which transformation can serve as a VST. We can analyse this relationship empirically by running a regression that explains the WIS (which approximates the CRPS) as a function of the central estimate of the predictive distribution. We ran the regression
\begin{linenomath*}
\begin{equation}
    \log[\text{WIS}(F, y)] = \alpha + \beta \times \log[\text{median}(F)], 
\end{equation}
\end{linenomath*}
where the predictive distribution $F$ and the observation $y$ are on the natural scale. This is equivalent to
\begin{linenomath*}
\begin{equation}
    \text{WIS}(F, y) = \exp(\alpha) \times \text{median}(F)^\beta, 
\end{equation}
\end{linenomath*}
meaning that we estimate a polynomial relationship between the predictive median and achieved WIS. Note that we are using predictive medians rather than means as only the former are available in the European COVID-19 Forecast Hub. As (under the simplifying assumption of normality; see the previous theoretical discussion on the mean-variance relationship) the WIS/CRPS of an ideal forecaster scales with the standard deviation, a value of $\beta = 1$ would imply a quadratic median-variance relationship; the natural logarithm could then serve as a VST. A value of $\beta = 0.5$ would imply a linear median-variance relationship, suggesting the square root as a VST. We applied the regression to case and death forecasts, stratified for one through four-week-ahead forecasts. Results are provided in Table \ref{tab:HUB-regression}. It can be seen that the estimates of $\beta$ always take a value somewhat below 1, implying a slightly sub-quadratic mean-variance relationship. The logarithmic transformation should thus approximately stabilize the variance (and WIS), possibly leading to somewhat higher scores for smaller forecast targets. The square-root transformation, on the other hand, can be expected to still lead to higher WIS values for targets of higher orders of magnitude.

\begin{figure}[h!]
    \centering
    \caption{Relationship between median forecasts and scores. Black dots represent WIS values for two-week ahead predictions of the EuroCOVIDhub-ensemble. Drawn in red are the regression lines as discussed in the main text and shown in Table \ref{tab:HUB-regression}. A: WIS for two-week-ahead predictions of the EuroCOVIDhub-ensemble against median predicted values. B: Same as A, with scores obtained after applying a square-root-transformation to the data. C: Same as A, with scores obtained after applying a log-transformation to the data.} 
    \label{fig:HUB-regression}
\end{figure}

@@

\paragraph{S3 Fig.}
\label{fig:score-approx}
\textbf{Visualisation of expected CRPS values against approximated scores.} 
This is using the approximation detailed in theoretical discussion on model rankings (see also Fig \ref{fig:SIM-wis-state-size-mean}). Expected CRPS scores are shown for three different distributions once on the natural scale (top row) and once scored on the log scale (bottom row).
